Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-19 Report/convergence_centralized.tex
updated

We now show that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To do this, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}. Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity} that 
\begin{equation} \label{seq_mon}
f(\ma^{t_{j+1}}) \leq f(\ma^{t_{j}}).
\end{equation}
%Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}. 
Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
\begin{equation} \label{limpoint}
\lim_{t \to \infty} f(\ma^{t}) = \lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).
\end{equation}

@@

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
\review{Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point. Now, we show that \eqn{\{\hat{f}(\ma^t)\}} is also convergent. Since \eqn{\{f(\mat{t}) \}} is monotonically decreasing, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}, therefore, we have
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|.
\end{equation}
Moreover, we know that \eqn{\{\hat{f}(\mat{t})\}} is bounded, therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be ensured.}

>>>>

We now show that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To do this, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}. Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity}, we have
\begin{equation} \label{seq_mon}
f(\ma^{t_{j+1}}) \leq f(\ma^{t_{j}}).
\end{equation}
%Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}. 
Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
\begin{equation} \label{limpoint}
\lim_{t \to \infty} f(\ma^{t}) = \lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).
\end{equation}

@@

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
\review{Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point. In order to ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}. Then, by using \eqref{mod_obj} and \eqref{strict_monotonicity}, monotonicity of \eqn{\{\hat{f}(\ma^t)\}} is shown by using \eqref{mod_obj} as
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|
\end{equation}
where \eqn{\tau^t} is as in \eqref{mod_obj}. Additionally, by using Appendix \ref{c-a}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by \cite[Prop. A.3]{bertsekas1999nonlinear}.}
